---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dataInspecter

<!-- badges: start -->
<!-- badges: end -->

The goal of dataInspecter is to read/load in the data, inspect data and save data. Plus it can also give the time.


# Functions
This package contains four functions that can be helpful for loading, inspecting and saving data. 

The four funtions are:
1: read_data_from_excel(). loads in data from excel and previews data
2: print_head(). shows the first 10 rows of the dataset
3: save_datafile(). saves variable as .csv and .rds
4: time(). tells the time

## Installation

You can install the development version of dataInspecter from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("kjettil/dataInspecter", build_vignettes = TRUE)
```

## Example

This is a basic example which shows you how to preview a dataset using print_head and saving the dataset as CSV and rds using save_datafile

```{r example}
library(dataInspecter)
dataset <- data.frame(X1 = c(1.5, 2.8, 3.2, 4.7),X2 = c(5.1, 6.2, 7.3, 8.4),X3 = c(9.9, 10.2, 11.5, 12.8))
print_head(dataset)

save_datafile(dataset, "test_dataset")
```

## Data
This package comes with a dataset that shows the tetracyclines consumption in the EU/EEA from 2011 till 2020. ?tetracyclines_usage will give you more detailed information about the dataset.

