---
title: "dataInspecter-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{dataInspecter-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(dataInspecter)
```

# Introduction

The goal of dataInspecter is to read/load in the data, inspect data and save data. Plus it can also give the time.


## Functions
This dataset contains four functions that can be helpful for loading, inspecting and saving data. 

The four funtions are:
1: read_data_from_excel(). loads in data from excel and previews data
2: print_head(). shows the first 10 rows of the dataset
3: save_datafile(). saves variable as .csv and .rds
4: time(). tells the time


# Installation

You can install the development version of dataInspecter from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("kjettil/dataInspecter")
```

# Usage
## Example 1: read_data_from_excel()
The read_data_from_excel function reads in data and also shows a preview after loading in the data. The first input is the name of the excelfile with extencion. The second input is the sheet. can be a number or a name. The last input is the range of the excel file, This allows you to select certain parts of the excel file. All inputs must be filled in

```{r}
# Generate test data
 test_file <- tempfile(fileext = ".xlsx")
test_data <- data.frame(X1 = c(1, 2, 3),X2 = c("A", "B", "C"))

# write dataset to .xlsx
writexl::write_xlsx(test_data, path = test_file)

# read excel file using read_data_from_excel()
read_data_from_excel(test_file, sheet = 1, range = "A1:B4")
```

## Example 2: print_head()

The print_head function prints the first (10) rows of a variable (dataset).
```{r}
 dataset <- data.frame(X1 = c(1.5, 2.8, 3.2, 4.7),X2 = c(5.1, 6.2, 7.3, 8.4),X3 = c(9.9, 10.2, 11.5, 12.8))
print_head(dataset)
```


## Example 3: save_datafile()

This function saves the dataset to a .csv and .rds. The first input is the variable that will be saved and the second input is the name you want to give it between qoutes ""

```{r}
dataset <- data.frame(X1 = c(1.5, 2.8, 3.2, 4.7), X2 = c(5.1, 6.2, 7.3, 8.4), X3 = c(9.9, 10.2, 11.5, 12.8))
save_datafile(dataset, "dataset")
```


## Example 4: time()

This functions gives the current time and puts it in a greeting

```{r}
time()
```

# Conclusion
Key features package:
- load and preview data
- show first 10 rows
- save data as .csv and .rds at the same time
- give the time

benefits:
This package and the functions are easy to use. the functions belong together and complement each other> this makes it easier to inspect, preview and save the data. 
- the time functions greets you when you ask for the time so thats a bonus.
Summarize the key features and benefits of your package. Provide any additional information or resources that may be helpful to the users.
